---
title: "Instructions"
author: "Nathan Riojas, Corey Monreal-Jackson, Ryan Billa"
date: "September 30, 2015"
output: html_document

---


#### Steps used to create this project
#####1. Using GitHub, create a Repo
#####2. Clone the Repository into the Data Visualization Folder (Or the folder you wish)
#####3. Create R Studio Folders for all the project development (folder descriptions below)
#####4. Locate a CSV data file and save it to the data folder
#####5. Modify the R_ETL.R given and run the code to get the code to develop a SQL table
#####6. Using Oracle SQL Developer, paste the code output from the R_ETL.R script to create a table
#####7. After the table is created, import the data from the CSV reformattted file to the table
#####8. Use a query statement similar to the TitanicAnalysis.R file (used in the last project) to build a data frame with the CSV data from Oracle 
#####9. Build 3 different workflows using R code and %>%. These will become new dataframes.
#####10. Generate unique plots from the workflow dataframes
#####11. Call these files in a .Rmd file using the R markdown command "source" and press Knit HTML to view the data/plots. (Code seen below) Note: Tables will also be generated to show the what the workflows created.

#### Folders Needed
#####00 Doc: Holds the .Rmd and .html files containing these instructions and project output. Also holds RPROFILE to load all required packages.
#####01 Data: Generates the code to create the table in Oracle. Gathers the data from the database for and puts it into data frames
#####02 Data Wrangling: Contains the .R files that use create workflows from the data frame create from the CSV data put into Oracle.
#####03 Visualization: Contains the .R files that use ggplot to generate graph our graphs


#### R markdown code
#####The .R file is called using the command below. The subsequent code/graphs illustrates the code that goes into

##### 

```{r warning = FALSE}
source("../00 Doc/RPROFILE.R", echo = TRUE)
source("../01 Data/Fortune500.R", echo = TRUE)
source("../01 Data/Fortune 500 Analysis.R", echo = TRUE)
source("../02 Data Wrangling/Fortune500 Wrangling.R", echo = TRUE)
source("../03 Visualizations/Companies Visualization.R", echo = TRUE)
```{r}
